Writing Trash Bin

### 2024-03-26 writingdumpster.qmd
sorted many notes and moved hurricane comment over

Cite Gap 3: Organise Uncertainty definitions
- Some consider it to be synonymous with specific terms defined in mathematics, such as probability [*HERE*], variance[*HERE*], error[*HERE*], or precision[*HERE*]. Others consider it to be an encompassing umbrella term of which for these mathematically defined objects are only examples[*HERE*], and include concepts that are somewhat related, such as missing values[*HERE*]
- This wide array of uncertainty definitions becomes a snake eating its own tail, as many authors opt to redefine uncertainty themselves[*HERE*], ignore defining uncertainty entirely [*HERE*], or pick a definition from a seemingly randomly previously published papers [*HERE*], all of which make variance in uncertainty definitions even worse

Cite Gap 4: Organise uncertainty quantification
- The uncertainty visualisation literature is completely awash with papers that define uncertainty using a vague encompassing phrase but go on to *quantify* uncertainty as a PDF, error, or some other easily quantified mathematical object when it comes time to do the visualisation.
- This definition swap happens so subtly that it seems to go unnoticed by authors writing the papers, and the fact that "uncertainty visualisation" methods dont even notice they are exclusively focus on depictions of easily quantifiable uncertainty, such as error [*HERE*], mass [*HERE*], or variance [*HERE*]
- Many papers will boast a title that claims to be about uncertainty visualisaiton, but simply depicts different visual representations of a PDF, however it takes reading the methodology to find this out

Cite Gap 6: This has left the expressions of uncertainty that are hard to quantify or visually differentiate untouched, despite many papers calling for their invention [*HERE*]

Cite Gap 7: Uncertainty Taxonomies
- Taxonomies split uncertainty based on an endless stream of arbitrary lines in the sand, such as whether the uncertainty is due to true randomness or a lack of knowledge [@Spiegelhalter2017 *HERE*], if the uncertainty is in the the attribute, spatial elements, or temporal element of the data [*HERE*], whether the uncertainty is scientific (e.g. error) or human (e.g. disagreement among parties) [*HERE*], if the uncertainty is random or systematic [*HERE*], statistical or bounded [], accuracy or precision [*HERE*], if the uncertainty is about the past or the future [*HERE*], the stage of the data analysis pipeline it comes from [*HERE*], the severity of the uncertainty [*HERE*], how quantifiable the uncertainty is [@Spiegelhalter2017], and many, many, many more examples.

Cite Gap 8: Bar/pie uncertainty graphics
- For example @Leland2005 mentions that popular graphics, such as pie charts and bar charts omit uncertainty, however at least one or both of these charts are used in most "uncertainty visualisation" experiments [@Ibrekk1987 *MORE HERE*]

Cite Gap 9: Other uncertainty vis taxonomies

Cite Gap 10: Reason uncertainty visualisation is different
- Papers will often discuss uncertainty in relation to one of these motivating reasons, the evaluation experiments motivated by (1) often perform different visualisations of PDFs, while the papers motivated by (2) will focus on trying to impute uncertainty as error within one of the existing channels, such as colour

Cite Gap 12: Equal information
- Visualisation authors are almost unanimous in commenting that the "information" in two plots must be the same in order for the visual techniques to be compared

Cite Gap 13: Examples of what is "information" in a visualisation

Cite Gap 14: Examples of mathematically obvious results

Cite Gap 15: Examples of replicated perceptual task experiments

Cite Gap 16: Examples of value extraction decision making tasks

Cite Gap 17: Examples of studies where the correct choice was to *ignore* the uncertainty information

Cite Gap 18: Examples of studies where authors measure trust

## Extra Section Cite Gaps
Cite Gap - New Section: Logical fallacy interpretation of mathematically unanswerable questions. If I tell you my cousins age, and then ask you to guess my age, it would not be unreasonable to guess the age I provided for my cousin. Citing this work to state "people incorrectly believe my cousins age is my age" would
- Deterministic questions about a random event cannot be answered. 
- @uncertchap2022 took the results of other paper to mean "when participants viewed mean temperature forecasts that included 95% confidence intervals depicted as bars with end caps, they incorrectly believed that the error bars represented high and low temperatures" (this one will depend on that study)

# Moved over notes
- These industry visualisation are likely made with a large amount of back and forth between different levels of an organisation, something that is important for good visual communication [@Spiegelhalter2017]. 
- @Boone2018 organised responses from participants by the approach they used and tried to account for participants prior beliefs (the method of eliciting prior beleifs was, however, questionable). 
- @Correll2018 “place your 5 ships on the safest locations on the board.” (minimise danger)
- @Blenkinsop2000 did try to include uncertainty as noise, asking participants to search for a specific outcome (the land classified as grass) in a random . However the participants failing to identify the signal (something that would be expected of an uncertainty plot) was seen as a sign the task was too complicated. While the task in this experiment *was* certainty far too complicated (and poorly communicated) this discussion indicates the authors did not consider the signal suppression to be the goal of the visualisation, and rather an annoying distraction. 
- @Ibrekk1987 expected participants to calculate the mean using a pie chart that had numerical bins combined (e.g. segment one was 0-2 inches of snow, and segment two was 2-4 inches of snow) so it could not be done by calculation. The authors also expected participants to use a CDF to calculate the mean, which needs to be converted *back* into a PDF to do so mathematically, so it was unclear how participants were supposed to do this calculation visually unless they were to just make a blind guess. The authors interpreted this as the participants misinterpreting how the CDF works, not seeming to realise they gave them an impossible task.
- @Blenkinsop2000 tailored their questions according to the visualisation shown, which implies an understanding that different visualisations contain different information. Despite this the authors still compared the visualisations according to which were "useful for uncertainty visualisation". 
- @Blenkinsop2000 asked different questions for each uncertainty visualisation, indicating they had some awareness that the question has a significant impact on whether or not the visualisation should be used.
- @Gschwandtnei2016 When answering “What is the statistical probability (in %) that the interval has already ended at the marked point in time (red line)?” many answers gave the estimated probability to which the marked point in time falls into the interval. This is correct when asking for the probability to which the interval has already started at the marked position. However, in case of the probability to which the interval has already ended at the marked position, this answer is the inverted probability of what we were looking for. They believe this is their own mistake so they so they don’t present these results.
- @Ibrekk1987 used several displays of a probability density functions, since “formally equivalent representations are often not psychologically equivalent”.
- @Ibrekk1987 highlights that in the face of a vague question, participants will use the plot to decide what the authors mean. 
@Sanyal2009 users performed significantly well using Glyph-size when the task was to search for locations of least uncertainty. However, both Glyph-color and Surface-color performed better than Glyph- size when the task was to search for locations of high uncertainty. We did not expect to find a significant difference between the two search tasks since both the tasks were designed to find extremes in the data
@Kim2019 believed an understanding of participants prior beliefs could assist in interpreting uncertainty visualisation results that tend to be incredibly noisy.
@Thomson2005 titled their paper "A typology for visualizing uncertainty" however it is a taxonomy for the specific types of uncertainty that we may want to visualise and a way to calculate that uncertainty. While this paper is more about mathematics than visualisation, it is clearly written as a precursor to visualisation.
- Some markers of probability that have common uses, probabilities such as 0 (impossible), 0.5 (a fair coin flip), 1 (certain) are easy for people to have an internal sense of *hullman paper*. 

@@

- @Munzner2009, in her nested model for visualisation, comments on how even something as low level as poor problem abstraction can cause down stream effects and become impossible to ignore. 
- @Otsuka2023 highlights that the choices made in the ontological process of boiling real world events down into statistical objects can influence later stages of analysis due to what was considred signal and what was considered noise. 
- @Meng2021 stresses the importance of treating data as an input from another process with noise and variance, rather than as a neutral input.
- @Griethe2006 mentions that there are detailled classifications of uncertainty but the literature and subsequent techniques are not ballanced, and instead concentrate on scalar values. In facing this lack of ballance she creates a new classification system for uncertainty visualisation. 
- @Griethe2006 commented that uncertainty appears at every step in the analyis pipeline, and commented on some the mathematical definitions that seek to quantify uncertianty, but did not explain how these mathematical definitions can be combined across levels. Unfortunately this quantification is needed since she mentioned that in order to visualise uncertainty, it needs to be measurable.
- @Griethe2006 defined uncertainty as "the degree to which the lack of knowledge about the amount of error is responsible for hesitancy in accepting results and observations without caution". 
- @Griethe2006 found that there there are two ways to visualise uncertianty, implicitly and explicitly. When a visualisaion is implicit, the uncertainty is considered an uninteresting feature of the data, and instead of mapping some quantification of uncertainty to a visual feature, data is filtered out if it does not meet a specified "certainty" threshold. These statements clearly points towards a signal/noise dichotomy with normal visualisation and uncertainty visualisation.
- @Spiegelhalter2017 common sentiments such as avoiding chart junk, considering a table in place of a visualsiaiton, use of narrative labels, managing emotion, less is more approach, etc, are the main concepts expressed. - @Spiegelhalter2017 suggests that the graphic should allow "part-to-whole" comparison on an appropriate scale, which seems to be an extension of the framing concept discussed when speaking about uncertainty communication more broadly.
- @Hullman2016 commented on the lack of justification of particular questions used in experiments and the lack of generalisability in using plot ranking as a response technique.
- @Hullman2016 discussed the lack of clarity in exactly what "uncertainty" authors are trying to ask about. Whether the participants are supposed to answer according to some ground truth or their subjective probability is unclear, as is whether the *uncertainty* depicted represents the uncertainty of a sampling or population distribution. 
- @Hullman2016 discussed the role of heuristics in the analysis of results and suggested authors look for signs of them in responses and ask subjects to describe their strategy in their response. 
- @Hullman2016 What was particularly interesting was people's tendancy to ignore uncertainty in a plot all together, and use a pattern in the signal (such as distance between means) to answer questions that require uncertainty information. 
- @Daradkeh2015 found that people tended to to make decisions on a small number of salient pieces of information rather than on systematic evaluations of the costs and benefits of choices.
- @Daradkeh2015 found that people tended to to make decisions on a small number of salient pieces of information rather than on systematic evaluations of the costs and benefits of choices.
@Daradkeh2015 found that people tended to ignore or give little weight probability information and instead focused on the severity of undersierable outcomes.
@Daradkeh2015 found that people tended to ignore or give little weight probability information and instead focused on the severity of undersierable outcomes.
- @wu2023rational attempted to remedy this issue caused by designing a "rational agent benchmark" such that participants in an experiment are compared to a rational agent. This suggestion is an insufficient band-aid solution that is built upon the same invalid assumptions as the rest of the literature, and simply digs the field deeper into these problems, rather than solve them. 
- @wu2023rational almost seems to recognise the problem of decision making experiments with payment schemes or correct/incorrect answers, but instead of understanding this boils these tasks down to value extraction, they suggest participants should be compared to a "rational agent". This rational agent acts as a benchmark, in the same way a ground truth statistic does for value extraction experiments, except the authors don't seem to realise that is what they have done. This paper highlights many decision making tasks are simply a value extraction experiment without realising it, this paper included.
- make sure quantified vs discussed uncertainty is mentioned

@@

- believed that offering enough decisions with varying rewards you can observe the true subjective probability, however whether or not probability is the right representation of subjective uncertainty is a topic of debate @Hullman2016
- she also discusses graphical interface (users have to draw the probability distribution) and framing probabilities as natural frequencies are better choices because they reduce noise and stuff.@Hullman2016
- Consider incorperating utility functions. Include "probability-coherence" checks @Hullman2016
- evidence that people do not follow the axioms of probability when conveying subjective probabilities. How do you deal with this as an analyst (e.g. if the probabilities do not sum to 1 @Hullman2016
- we consider a summary table as a visualisation, illuminate graphics with words and numbers, design graphics to allow a part-to-whole comparison on an appropriate scale, use images and metaphors to gain/retain attention but dont arouse undue emotion, assume low numeracy of a general public audience and adopt a less-is-more approach by reducing the need for inference and making clear and explicit comparison, be cautious about interactivity and animations (may introduce unnecessary complexity), avoid chart junk (like 3d bar charts) @Spiegelhalter2017
- @Maceachren2012 found to be the worst aesthetics to map to uncertainty to as they don't have an intuitive interpretation.
- @Bella2005 found that most participants were ignorant to the fact that error bars are used for both confidence intervals and standard error bars, two wildly different indicators of precision. (**also the paper sherry sent me**)
- Several studies probide evidence that the usability of uncertainty representations can be highly user and task dependent @Kinkeldey2014
- The tasks for participants were most commonly value retrival (some where uncertainty and data value are retrived separately, others where they are some separately). also also be asked to extract a relative value @Kinkeldey2014
- most studies used coincident approaches, static visualisations, are applied to a specific domain and dont have generalised results @Kinkeldey2014
- Most studies involve intrinsic approaches such as colour, transparency, and those that used extrinsic techniques typically used glyphs, error bars, grid based techniques, or contouring @Kinkeldey2014
- Mentioned alleatory vs epistemic uncertainty, in the visualisation literature alleatory uncertainty is more commonly the focus. also mentions dependence and joint pdfs as a consideration @Hullman2016
- When asking questions, researchers should focus on events that can be repeated (because of a misunderstanding of confidence intervals) @Hullman2016 (moved here because it is clear she is touching on the whole "what are we uncertain about" thing)
- we should aim to show enough information to solve a task while avoiding irrelevant distracting information [@kosslyn2006graph]. 
- people will discount information they perceive as discountable if they are able. Including mean estimates on depictions of mass can cause people to discount the uncertainty information and use the difference between means as a proxy for the probability distribution [@Kale2021].
- rarely used extension is aggregation of uncertainty over an area (retrieve overall estimation from a spatial distribution of uncertainty). Other tasks include comparisons, rankings. also have a task called "search" where participants have to identify entities that fulfill certainty characteristics (high or low values) @Kinkeldey2014
- Whether to use classed or unclassed uncertainty is rarely discussed @Kinkeldey2014. e.g. land map with remotely sensed images has ambiguity in the boundaries, which can result from multiple sources (land cover class, measurement error, images from different dates). If you combine them all it might not make sense for someone who only needs one.
- The way we ask questions and the types of questions we ask are selected with little justification. This paper makes suggestions to reduce the noise in the data from these papers. @Hullman2016
- Error is best mapped to fuzziness, location, and colour value; arrangement, size and transparency are an OK second choice; but saturation, hue, orientation and shape are unacceptable and have no intuitive connection to variance [@Maceachren2012]. 
- @Nathonours found that a scatter plot is better than a line plot if you want to convey the correlation between two time series but we cannot be sure if this was influenced by swapping the distribution depicted or by dropping the irrelevant feature of inexchangeability.
- No only do the graphical elements we map our features to matter, but the direction matters too. Graphical elements that are more fuzzy (fuzziness), further from centre (location), lighter (colour value), poorly arranged (arrangement), smaller (size), more transparent (transparency) are perceived to be more uncertain [@Maceachren2012]. 
- This idea also extends to interval estimation, where questions about probability are best answered with gradients and questions about start and end times are easiest to answer with ambiguation [@Gschwandtnei2016].

>>>>

### Cite Gap 3: Uncertainty definition + signal supression
> Some consider it to be synonymous with specific terms defined in mathematics, such as probability [*HERE*], variance[*HERE*], error[*HERE*], or precision[*HERE*]. Others consider it to be an encompassing umbrella term of which for these mathematically defined objects are only examples[*HERE*], and include concepts that are somewhat related, such as missing values[*HERE*]
> This wide array of uncertainty definitions becomes a snake eating its own tail, as many authors opt to redefine uncertainty themselves[*HERE*], ignore defining uncertainty entirely [*HERE*], or pick a definition from a seemingly randomly previously published papers [*HERE*], all of which make variance in uncertainty definitions even worse

- @Thomson2005 titled their paper "A typology for visualizing uncertainty" however it is a taxonomy for the specific types of uncertainty that we may want to visualise and a way to calculate that uncertainty. While this paper is more about mathematics than visualisation, it is clearly written as a precursor to visualisation.
- @Griethe2006 commented that uncertainty appears at every step in the analyis pipeline, and commented on some the mathematical definitions that seek to quantify uncertianty, but did not explain how these mathematical definitions can be combined across levels. Unfortunately this quantification is needed since she mentioned that in order to visualise uncertainty, it needs to be measurable.
- @Griethe2006 defined uncertainty as "the degree to which the lack of knowledge about the amount of error is responsible for hesitancy in accepting results and observations without caution".

### Cite Gap 4: Organise uncertainty quantification
> The uncertainty visualisation literature is completely awash with papers that define uncertainty using a vague encompassing phrase but go on to *quantify* uncertainty as a PDF, error, or some other easily quantified mathematical object when it comes time to do the visualisation.
> This definition swap happens so subtly that it seems to go unnoticed by authors writing the papers, and the fact that "uncertainty visualisation" methods dont even notice they are exclusively focus on depictions of easily quantifiable uncertainty, such as error [*HERE*], mass [*HERE*], or variance [*HERE*]
> Many papers will boast a title that claims to be about uncertainty visualisaiton, but simply depicts different visual representations of a PDF, however it takes reading the methodology to find this out

### Cite Gap 6: All PDF no Missing values
> This has left the expressions of uncertainty that are hard to quantify or visually differentiate untouched, despite many papers calling for their invention [*HERE*]

- @Griethe2006 mentions that there are detailled classifications of uncertainty but the literature and subsequent techniques are not ballanced, and instead concentrate on scalar values. In facing this lack of ballance she creates a new classification system for uncertainty visualisation. 
- Mentioned alleatory vs epistemic uncertainty, in the visualisation literature alleatory uncertainty is more commonly the focus. also mentions dependence and joint pdfs as a consideration @Hullman2016

### Cite Gap 7: Uncertainty Taxonomies
> Taxonomies split uncertainty based on an endless stream of arbitrary lines in the sand, such as whether the uncertainty is due to true randomness or a lack of knowledge [@Spiegelhalter2017 *HERE*], if the uncertainty is in the the attribute, spatial elements, or temporal element of the data [*HERE*], whether the uncertainty is scientific (e.g. error) or human (e.g. disagreement among parties) [*HERE*], if the uncertainty is random or systematic [*HERE*], statistical or bounded [], accuracy or precision [*HERE*], if the uncertainty is about the past or the future [*HERE*], the stage of the data analysis pipeline it comes from [*HERE*], the severity of the uncertainty [*HERE*], how quantifiable the uncertainty is [@Spiegelhalter2017], and many, many, many more examples.

### Cite Gap 8: Bar/pie uncertainty graphics
> For example @Leland2005 mentions that popular graphics, such as pie charts and bar charts omit uncertainty, however at least one or both of these charts are used in most "uncertainty visualisation" experiments [@Ibrekk1987 *MORE HERE*]

### Cite Gap 9: Vis uncertainty Taxonomies
- Most studies involve intrinsic approaches such as colour, transparency, and those that used extrinsic techniques typically used glyphs, error bars, grid based techniques, or contouring @Kinkeldey2014

### Cite Gap 10: High dimensional vs psychological
> Papers will often discuss uncertainty in relation to one of these motivating reasons, the evaluation experiments motivated by (1) often perform different visualisations of PDFs, while the papers motivated by (2) will focus on trying to impute uncertainty as error within one of the existing channels, such as colour

### Cite Gap 12 & 13 & 14: Information & Mathematical stuff
- we should aim to show enough information to solve a task while avoiding irrelevant distracting information [@kosslyn2006graph]. 
- @Ibrekk1987 used several displays of a probability density functions, since “formally equivalent representations are often not psychologically equivalent”.
- @Hullman2016 commented on the lack of justification of particular questions used in experiments and the lack of generalisability in using plot ranking as a response technique.
- @Hullman2016 discussed the lack of clarity in exactly what "uncertainty" authors are trying to ask about. Whether the participants are supposed to answer according to some ground truth or their subjective probability is unclear, as is whether the *uncertainty* depicted represents the uncertainty of a sampling or population distribution. 
- @Bella2005 found that most participants were ignorant to the fact that error bars are used for both confidence intervals and standard error bars, two wildly different indicators of precision. (Note: Uncertainty intervals can only be validly compared to a constant value, you compare Data to a theoretical distribution, OR uncertainty to a theoretical threshold (not data). The participants should convert the distributions to A - B and then see if the 95% of THAT distribution overlaps with 0)
- @Blenkinsop2000 tailored their questions according to the visualisation shown, which implies an understanding that different visualisations contain different information. Despite this the authors still compared the visualisations according to which were "useful for uncertainty visualisation". 
- When asking questions, researchers should focus on events that can be repeated (because of a misunderstanding of confidence intervals) @Hullman2016 (moved here because it is clear she is touching on the whole "what are we uncertain about" thing)

### Cite Gap 15: Value Extraction (Examples of replicated perceptual task experiments)
- @Correll2018 “place your 5 ships on the safest locations on the board.” (minimise danger) It is a convoluted value extraction task, where participants basicaly have to look at the palette and see that if it is in the lower uncertainty, and lower error it is better, but higher uncertainty is better
- @Ibrekk1987 expected participants to calculate the mean using a pie chart that had numerical bins combined (e.g. segment one was 0-2 inches of snow, and segment two was 2-4 inches of snow) so it could not be done by calculation. The authors also expected participants to use a CDF to calculate the mean, which needs to be converted *back* into a PDF to do so mathematically, so it was unclear how participants were supposed to do this calculation visually unless they were to just make a blind guess. The authors interpreted this as the participants misinterpreting how the CDF works, not seeming to realise they gave them an impossible task.
- @Sanyal2009 users performed significantly well using Glyph-size when the task was to search for locations of least uncertainty. However, both Glyph-color and Surface-color performed better than Glyph- size when the task was to search for locations of high uncertainty. We did not expect to find a significant difference between the two search tasks since both the tasks were designed to find extremes in the data
- The tasks for participants were most commonly value retrival (some where uncertainty and data value are retrived separately, others where they are some separately). also also be asked to extract a relative value @Kinkeldey2014

### Cite Gap 16: Decision making stuff 
- @Boone2018 organised responses from participants by the approach they used
- @Hullman2016 suggested authors look for signs of heuristics in responses and ask subjects to describe their strategy in their response. 
- @Hullman2016 What was particularly interesting was people's tendancy to ignore uncertainty in a plot all together, and use a pattern in the signal (such as distance between means) to answer questions that require uncertainty information. 
- @Kim2019 believed an understanding of participants prior beliefs could assist in interpreting uncertainty visualisation results that tend to be incredibly noisy.
- @Daradkeh2015 found that people tended to to make decisions on a small number of salient pieces of information rather than on systematic evaluations of the costs and benefits of choices.
- @Daradkeh2015 found that people tended to ignore or give little weight probability information and instead focused on the severity of undersierable outcomes.
- believed that offering enough decisions with varying rewards you can observe the true subjective probability, however whether or not probability is the right representation of subjective uncertainty is a topic of debate @Hullman2016
- she also discusses graphical interface (users have to draw the probability distribution) and framing probabilities as natural frequencies are better choices because they reduce noise in responses [@Hullman2016]
- Consider incorporating utility functions. Include "probability-coherence" checks [@Hullman2016]
- evidence that people do not follow the axioms of probability when conveying subjective probabilities. How do you deal with this as an analyst (e.g. if the probabilities do not sum to 1 @Hullman2016

### Cite Gap 17: Please Ignore uncertainty
- @Blenkinsop2000 did try to include uncertainty as noise, asking participants to search for a specific outcome (the land classified as grass) in a random . However the participants failing to identify the signal (something that would be expected of an uncertainty plot) was seen as a sign the task was too complicated. While the task in this experiment *was* certainty far too complicated (and poorly communicated) this discussion indicates the authors did not consider the signal suppression to be the goal of the visualisation, and rather an annoying distraction.

### Cite Gap 18: Trust stuff

# Additions

### Addition topic 1: Logical fallacy interpretation of mathematically unanswerable questions. 
- If I tell you my cousins age, and then ask you to guess my age, it would not be unreasonable to guess the age I provided for my cousin. Citing this work to state "people incorrectly believe my cousins age is my age" would
- Deterministic questions about a random event cannot be answered. 
- @uncertchap2022 took the results of other paper to mean "when participants viewed mean temperature forecasts that included 95% confidence intervals depicted as bars with end caps, they incorrectly believed that the error bars represented high and low temperatures" (this one will depend on that study)
- @Boone2018 the method of eliciting prior beleifs was, however questionable. Said people did or did not think something was likely but the question was weird.

### Addition topic 2: Uncertainty vis communication considerations
#### Unvertainty
- Some markers of probability that have common uses, probabilities such as 0 (impossible), 0.5 (a fair coin flip), 1 (certain) are easy for people to have an internal sense of [@Hullman2016]

@@

@@

#### Visualisation
- @Spiegelhalter2017 common sentiments such as avoiding chart junk, considering a table in place of a visualsiaiton, use of narrative labels, managing emotion, less is more approach, etc, are the main concepts expressed. 
- @Spiegelhalter2017 suggests that the graphic should allow "part-to-whole" comparison on an appropriate scale, which seems to be an extension of the framing concept discussed when speaking about uncertainty communication more broadly.
- @Hullman2016 discussed the role of heuristics in the analysis of results
- we consider a summary table as a visualisation, illuminate graphics with words and numbers, design graphics to allow a part-to-whole comparison on an appropriate scale, use images and metaphors to gain/retain attention but don't arouse undue emotion, assume low numeracy of a general public audience and adopt a less-is-more approach by reducing the need for inference and making clear and explicit comparison, be cautious about interactivity and animations (may introduce unnecessary complexity), avoid chart junk (like 3d bar charts) @Spiegelhalter2017
- @Maceachren2012 found __????_ to be the worst aesthetics to map to uncertainty to as they don't have an intuitive interpretation.

### Addition topic 3: Power of uncert vis (why it failled)
- @Suh2023 found that the main issue with deployment of AI was communication between data science and subject matter experts, since subject matter experts didn't want technical presentations that didn't explain exactly when and how a model would fail.

### Addition topic 5: Participants getting confused by overcomplicated tasks
- @Gschwandtnei2016 When answering “What is the statistical probability (in %) that the interval has already ended at the marked point in time (red line)?” many answers gave the estimated probability to which the marked point in time falls into the interval. This is correct when asking for the probability to which the interval has already started at the marked position. However, in case of the probability to which the interval has already ended at the marked position, this answer is the inverted probability of what we were looking for. They believe this is their own mistake so they so they don’t present these results.
- @Ibrekk1987 highlights that in the face of a vague question, participants will use the plot to decide what the authors mean.

### Addition topic 5: Context stuff
- most studies used coincident approaches, static visualisations, are applied to a specific domain and dont have generalised results @Kinkeldey2014

# Moved over notes
- people will discount information they perceive as discountable if they are able. Including mean estimates on depictions of mass can cause people to discount the uncertainty information and use the difference between means as a proxy for the probability distribution [@Kale2021].
- rarely used extension is aggregation of uncertainty over an area (retrieve overall estimation from a spatial distribution of uncertainty). Other tasks include comparisons, rankings. also have a task called "search" where participants have to identify entities that fulfill certainty characteristics (high or low values) @Kinkeldey2014
- Whether to use classed or unclassed uncertainty is rarely discussed @Kinkeldey2014. e.g. land map with remotely sensed images has ambiguity in the boundaries, which can result from multiple sources (land cover class, measurement error, images from different dates). If you combine them all it might not make sense for someone who only needs one.
- The way we ask questions and the types of questions we ask are selected with little justification. This paper makes suggestions to reduce the noise in the data from these papers. @Hullman2016
- Error is best mapped to fuzziness, location, and colour value; arrangement, size and transparency are an OK second choice; but saturation, hue, orientation and shape are unacceptable and have no intuitive connection to variance [@Maceachren2012]. 
- @Nathonours found that a scatter plot is better than a line plot if you want to convey the correlation between two time series but we cannot be sure if this was influenced by swapping the distribution depicted or by dropping the irrelevant feature of inexchangeability.
- No only do the graphical elements we map our features to matter, but the direction matters too. Graphical elements that are more fuzzy (fuzziness), further from centre (location), lighter (colour value), poorly arranged (arrangement), smaller (size), more transparent (transparency) are perceived to be more uncertain [@Maceachren2012]. 
- This idea also extends to interval estimation, where questions about probability are best answered with gradients and questions about start and end times are easiest to answer with ambiguation [@Gschwandtnei2016].
